Thesis Title

### 2023-03-13 chapters/thesis_outline.tex
Updates from Overleaf

\textbf{Part I} of the results, named “\textit{Applying metagenomics in the clinical context}”, includes \textbf{Chapters 2, 3 and 4}, where metagenomics is applied to both clinical and environmental samples. In the two first chapters, the performance of metagenomics to identify pathogens and antimicrobial resistance genes was evaluated. Importantly it was recognized that there was a lack of standardisation in the bioinformatic metagenomics analysis, so a fully reproducible workflow was developed for the streamlined analysis of human samples for genomic characterization in the context of Dengue infections, as a model for other applications.

>>>>

\textbf{Part I} of the results, named “\textit{Applying metagenomics in the clinical context}”, includes \textbf{Chapters 2, 3 and 4}, where metagenomics is applied to both clinical and environmental samples. In the two first chapters, the performance of metagenomics to identify pathogens and antimicrobial resistance genes was evaluated. Importantly it was recognised that there was a lack of standardisation in the bioinformatic metagenomics analysis, so a fully reproducible workflow was developed for the streamlined analysis of human samples for genomic characterization in the context of Dengue infections, as a model for other applications.
